Exploring mathematical objects from custom-tailored mathematical universes

### 2022-04-06 paper-filmat.tex
typo (thanks to Lukas!)

\subsection{The logic of toposes}\label{sect:logic-of-toposes}
By their definition as special kinds of
categories, toposes are merely algebraic structures not unlike groups or vector
spaces. Hence we need to argue why we picture toposes as mathematical universes
while we do not elevate other kinds of algebraic structures in the same way.
For us, this usage is justified by the following metatheorem:

@@

not be equivalent. This inbalance has mathematical applications and is explored

>>>>

\subsection{The logic of toposes}\label{sect:logic-of-toposes}
By their definition as special kinds of
categories, toposes are merely essentially algebraic structures not unlike groups or vector
spaces. Hence we need to argue why we picture toposes as mathematical universes
while we do not elevate other kinds of algebraic structures in the same way.
For us, this usage is justified by the following metatheorem:

@@

not be equivalent. This imbalance has mathematical applications and is explored
